%!TEX root = project.tex

\chapter{Conclusion}

With the project at the stage it is at this moment, it can be considered complete as there is no time remaining to continue the project. Many aspects of the project had worked as we had expected and other aspects of the project were harder or almost impossible, from the design stage to the implementation.
When we started the project, it was the biggest project that we have ever undertaken as programmers and because of this, we had no idea really what to expect from a group project of this type. We designed and implemented the project with the level of experience and understand that we had at that time. if we were to start this project today, we would definitely approach the project differently.\newline

One aspect we would change was the methodology, we used a waterfall method. This was taken due to the unpredictable lifestyle of a student, we didn't know exactly what issues we would face each week. At the start of the project, during semester 1, we didn't know the timetable that we would have during the second semester. We would not know the volume of projects that we would undertake during the year or the level of complexity each project would entail. For these reasons, the waterfall methodology seemed like a good fit. However, on reflection the agile methodology would have been ideal for a system that was as heterogeneous at this project. It would have been ideal to break the project down to its smaller components, and program these parts individually as completely detached programs from the system as a whole.\newline

A lot of portions of the game have been left unfinished, If we had designed a less heterogeneous system, we could have focused on one type of database and accompanying language, this would have allowed more time to finish the inner workings of the game. This is not something that we would have changed as we believe that learning to create these multiple systems that interconnect is more valuable than having a finished game. Finishing the game would, at this point only be a grouping of smaller fixes in bugs and implementation of small enhancements in the game.\newline