%!TEX root = project.tex

\chapter{Technology Review}

\input{TexFiles/unity.tex}

\input{TexFiles/VirtualReality.tex}

\section {Java}
Java is a high-level programming language developed by Sun Microsystems. It was originally designed for developing programs for set-top boxes and handheld devices, but later became a popular choice for creating web applications. The syntax is similar to that of C++ but it is strictly an object orientated programming language. Java programs contain classes and methods. Classes are used to define objects and methods are assigned to individual classes.\newline

Java programs are not run directly by the operating system. Instead, Java programs are interpreted by the JVM, Java Virtual Machine, which can be run on multiple platforms. This means all Java programs can be run on different platforms such as Mac, Windows and Unix computers.  In order for Java applications or applets to run at all the JVM must be installed.\newline

\section {C\#}
C\# is an object orientated programming language used for networking, web and game development. Dutch developer Anders Hejlsberg formed a team in 1999 during the development of the .NET framework to create a new C like Object Orientated Language (COOL).
\newline

C\# is used to develop robust applications through the .NET framework. C\# is a very similar language to java and C++ and generally developers who are familiar with java can adapt to C\# very quickly. C\# is the programming language used for game development in Unity.
\newline

\section {Go Lang}
Go Lang was conceived by Robert Griesemer, Rob Pike and Ken Thompson when they started sketching the goals for a new language on a white board on September 21, 2007. By January 2008, Ken Thompson had started working on a compiler with which to explore ideas. The compiler generated C code as its output. By mid 2008 the language had become a full-time project and had settled enough to attempt a production compiler. Go became a public open source project on November 10, 2009. There are now millions of Go programmers, or gophers, around the world. Go's success has far exceeded all expectations.\newline

At the time of Go's inception, only a decade ago, the programming world was very different from today. Production software was usually written in C++ or Java, GitHub did not even exist and most computers were not yet capable to run complex algorithms, and IDEs such as Visual Studio and Eclipse were the only real option. Throughout its design, Google have endeavoured to reduce clutter and complexity. There are no forward declarations and no header files as everything is declared exactly once. Go Lang is a relative new, yet popular language and seems to be on the rise in terms of application development.\newline


\section {Python}
The Python programming language was created by dutch programmer Guido Van Rossum who started developing the new script in the late 1980s and finally introduced the first version of that programming language in 1991. Today, it is developed by the Python Software Foundation. Python is a multi-paradigm language, Python programmers can accomplish their tasks using different styles of programming: object oriented, imperative, functional or reflective. \newline

Here are some of the principles that python is based on:\newline
\begin{itemize}
\item Beautiful is better than ugly
\item Simple is better than complex
\item Complex is better than complicated
\item Readability counts
\item In the face of ambiguity, refuse the temptation to guess
\item There should be one, and preferably only one, obvious way to do it
\item If the implementation is hard to explain, it’s a bad idea
\end{itemize}
\newline

Python has seen somewhat of a resurgence in recent years as an effective programming language for machine learning and the development of neural networks as we recently discovered through our Emerging Technology module.
\newline

\section {MongoDB}
Mongodb is an open source non relational database management system. MongoDB was created by Dwight Merriman and Eliot Horowitz, who had encountered development and scalability issues with traditional relational database approaches while building web applications at DoubleClick, an online advertising company that is now owned by Google Inc. The name of the database was derived from the word humongous to represent the idea of supporting large amounts of data.\newline

MongoDB uses collections and documents unlike relational databases that use tables and rows. A record in MongoDB is a document that contains a data structure made up of field and value pairs. MongoDB documents use a varient similar to JavaScript Object Notation (JSON) called Binary JSON known as BSON that allows for more data types. The fields in the documents are similar to columns in a relational databse and they can hold a large variety of data including other documents to arrays of documents.\newline

Documents in MongoDB must use a primary key as a unique identifier.
The (id field) is added by MongoDB to uniquely identify the document in the collection i.e.(id, Name, Address) id is the object id/primary key. Collections contain sets of documents and act as the equivalent of tables in a relational database.\newline

MongoDB does not require predefined schemas and it stores any type of data. Tihs provides scalability and felxibility compared to relational databases which makes it a useful database for companies running big data applications. One of the advantages of using documents is that these objects map to native data types in a number of programming languages. Also, having embedded documents reduces the need for database joins.\newline

MongoDB is available in community and commercial versions through vendor MongoDB Inc. MongoDB Community Edition is the open source release, while MongoDB Enterprise Server brings added security features.\newline
\cite{S174228761630031720160601}
\bibliographystyle{plain}
\section {Redis DB}
Redis (REmote DIctionary Server) is an open source (BSD licensed), in-memory data structure store, used as a database. It supports a large variety of different types of data that can be stored ranging from strings and lists to hashes and sorted sets. Redis allows you to run atomic operations on these types, like appending a string, increment the value in a hash, pushing an element to a list, computing set intersection, union and difference or getting the member with highest ranking in a sorted set.
\newline

Key features of redis are:\newline
High-Level Data Structures:  Provides five possible data types for values: strings, lists, sets, hashes, and sorted sets. Operations that are unique to those data types are provided and come with well documented time-complexity (Big O notation).\newline

High Performance:  Due to its in-memory nature, the project maintainer’s commitment to keeping complexity at a minimum, and an event-based programming model, Redis boasts exceptional performance for read and write operations.\newline

Lightweight With No Dependencies:  Written in ANSI C, and has no external dependencies. Works well in all POSIX environments. Windows is not officially supported, but an experimental build is provided by Microsoft.\newline

\section {MariaDB}
MariaDB is an open source relational database management system (DBMS). MariaDB is the compatible drop-in replacement for the widely used MySQL database technology. MariaDB intends to have high compatibility with MySQL and exact matching with MySQL APIs and commands. MariaDB's API and protocol are compatible with those used by MySQL, and also some other features to support local non-blocking operations and progress reporting.\newline

MariaDB is developing continuously and any new updates are transmitted to end users very fast with updated features like bug tracking that can be viewed in detail. They also offer a cluster database intended for commercial use that enables multi-master replication.\newline

MARIADB VS MYSQL\newline
\begin{itemize}
\item MariaDB has superior query performance.
\item MariaDB has a more open source attitude.
\item Making the switch to MariaDB is very easy.
\item Galera implementation is better in MariaDB.
\item MariaDB is available as an option with some hosting environments, like RackSpace Cloud.
\end{itemize}
\newline

\section {AWS}
Amazon Web Services (AWS), the pioneering cloud computing platform provided by Amazon.com, emerged from separate internal initiatives at Amazon over 16 years ago to both aid developers and also improve the efficiency of the company’s own infrastructure.\newline

Publicly launched on March 19, 2006, AWS offered Simple Storage Service (S3) and Elastic Compute Cloud (EC2). By 2009, S3 and EC2 were launched in Europe, the Elastic Block Store (EBS) was made public, and a powerful content delivery network (CDN), Amazon CloudFront, all became formal parts of AWS offering. These developer-friendly services attracted cloud-ready customers and set the table for formalized partnerships with data-hungry enterprises such as Dropbox, Netflix, and Reddit, all before 2010.\newline

\section {Docker}
Docker is an open platform for developing, shipping, and running applications. Docker enables you to separate your applications from your infrastructure so you can deliver software quickly. Docker provides the ability to package and run an application in a loosely isolated environment called a container. The isolation and security allow you to run many containers simultaneously on a given host.
\newline

Containers are lightweight because they don’t need the extra load of a hypervisor, but run directly within the host machine’s kernel. This means you can run more containers on a given hardware combination than if you were using virtual machines. You can even run Docker containers within host machines that are actually virtual machines.

\section {JSON}
JSON stands for Java Script Object Notation. JSON is a lightweight format for the storing of and transporting of data. JSON is a text format language that is completely language independent. JSON is used mainly to transfer data between a server and web or mobile applications. 
\cite{S235271101830050520190101}
\bibliographystyle{plain}
\newline



