%!TEX root = project.tex

\section {Unity 3D}
Unity 3D is a a game development environment created by David Helgason who setup Unity Technologies. 59\% of all virtual reality games are made using the Unity 3D engine. Unity works on 30 platforms, including Windows, iOS, Android, Nintendo Switch, Playstation 4, Oculus Rift, etc. Unity competes with Epic’s Unreal Engine, the game engine behind Fortnite and many games on the PS4 and Xbox One. 50\% of all games are made using Unity 3D. As we are making a virtual reality game, the two engines we could use are the Unity 3D engine or the Unreal 4 engine. Though the Unreal engine creates very beautiful games and is very well optimised, the programming language is C++. We have  never used C++ and starting a new language would make the process more complex. The Unity engine used the C\# language, which we have used previously.

\section {Unity UNET}
UNet is a feature in Unity that allows the programmer to create multiplayer or networked games over a network. It accomplishes this by allowing one player or service to act as a host or dedicated host. A standard host is also a client, a dedicated host is just a server and does not have a client connection. Each client sends data to the host and receives all data from the host instead of communicating with the other clients. UNet as of 2018 is deprecated and is planned to be replaced, although there is no information yet on its replacement. Part of the reason for UNet being replaced is due to data being sent from client to server, then to all other clients and has a latency issue as expected due to the path the data uses, as latency is usually the amount of time it takes for data to travel from client to server and back. This can be seen even in our program, when a player jumps their character, the players character can be seen stuttering but doesn't have such a noticeable effect when the character is not jumping.